Implicit yaddayadda

### 2011-10-27 papers/PLDI2012/implicitization.tex
Déplacement du résumé de l'algo de « Adding new paths » vers l'intro de 3.
Au passage, l'ordre des étapes n'était plus bonne par rapport au nouvel algo.

\begin{algorithm}
  \begin{algorithmic}
    \STATE \textit{Subset} $\gets \emptyset$
    \WHILE{true}
    \STATE Add new paths to \textit{Subset} (lines~\ref{alg=start-add-paths}-\ref{alg=end-add-paths} in algorithm~\ref{algo:combined})
    \STATE Ascending iteration on \textit{Subset} (lines~\ref{alg=start-ascending}-\ref{alg=end-ascending} in algorithm~\ref{algo:combined})
    \STATE Narrow (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined})
    \ENDWHILE
  \end{algorithmic}
\end{algorithm}

@@

Since we do not work on the entire transition graph but on a subset of it, we
conjoin the formula $f(p_i)$ with the actual set of working paths,
noted $P$, expressed as a Boolean formula, where the Boolean variables are the
\emph{reachability predicates} of the control points. We can easily construct
this formula from the binary decision diagram using dynamic programming, and
avoiding an exponentially sized formula. In other words, we force the SMT solver
to give us a path included in $P$.

@@

We distinguish two phases when analyzing a subgraph $P$:
\begin{enumerate}
\item We search for paths starting at point $p_i \in P_R$, such that these paths
	are in $P$, i.e are included in the working subgraph. Each time we find a
	path, we update the abstract value of the destination point of the path.
	This is the phase explained in \ref{subsec:ascending}.
\item  When the previous phase terminates, there are no more paths in
$P$, starting at $p_i$, 
that make the abstract values of the successors grow (otherwise, the SMT
solver would not have answered ``\emph{unsat}''). Narrowing iterations preserve
this property. 
However, there may exist such paths in the entire multigraph, that are not in
$P$. The second phase
computes these paths and adds them to $P'$ (line~\ref{alg=computeNewPaths} in
algorithm~\ref{algo:combined}). We also use SMT solving to discover
these new paths, but we slightly change the SMT formula given to the SMT solver:
we now simply check for the satisfiability of $f(p_i)$ instead of $f(p_i) \wedge
P$. Since we already know that $f(p_i) \wedge P$ is unsatisfiable, all
the paths given by the SMT solver won't be in $P$.
\end{enumerate}

>>>>

We distinguish three phases in the main loop of the analysis:
\begin{enumerate}
\item Whe start finding a relevant subset $P \cup P'$ of the graph.
  Either the previous iteration or the initialization lead us to a
  state where there are no more paths in the previous subset $P$,
  starting at $p_i$, that make the abstract values of the successors
  grow (otherwise, the SMT solver would not have answered
  ``\emph{unsat}''). Narrowing iterations preserve this property.
  However, there may exist such paths in the entire multigraph, that
  are not in $P$. This phase computes these paths and adds them to
  $P'$ (line~\ref{alg=computeNewPaths} in
  algorithm~\ref{algo:combined}). We also use SMT solving to discover
  these new paths, but we slightly change the SMT formula given to the
  SMT solver: we now simply check for the satisfiability of $f(p_i)$
  instead of $f(p_i) \wedge P$. Since we already know that $f(p_i)
  \wedge P$ is unsatisfiable, all the paths given by the SMT solver
  won't be in $P$. This phase is described in~\ref{subsec:addingpaths}
  and corresponds to lines in~\ref{alg=start-add-paths} to
  \ref{alg=end-add-paths} algorithm~\ref{algo:combined}.
\item Given a new subset $P$, we search for paths starting at point
  $p_i \in P_R$, such that these paths are in $P$, i.e are included in
  the working subgraph. Each time we find a path, we update the
  abstract value of the destination point of the path. This is the
  phase explained in~\ref{subsec:ascending}, and corresponds to
  lines~\ref{alg=start-ascending} to~\ref{alg=end-ascending} in
  algorithm~\ref{algo:combined}.
\item We perform narrowing iterations the usual way
  (line~\ref{alg=narrowing} in algorithm~\ref{algo:combined}) and
  reiterate from step 1 unless there are no more states to explore.
\end{enumerate}

@@

The difference with~\citet{Monniaux_Gonnord_SAS11} is that we do not
work on the entire transition graph but on a subset of it. Therefore we
conjoin the formula $f(p_i)$ with the actual set of working paths,
noted $P$, expressed as a Boolean formula, where the Boolean variables are the
\emph{reachability predicates} of the control points. We can easily construct
this formula from the binary decision diagram using dynamic programming, and
avoiding an exponentially sized formula. In other words, we force the SMT solver
to give us a path included in $P$.

@@

\MM{Cette partie est devenue toute petite, il y avait un résumé global
  de l'algo ici. Ça me parait suffisant comme ça}
